DeepSphere: a graph-based spherical CNN

### 2019-09-24 main.tex
Updates from Overleaf

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage[export]{adjustbox} % figure vertical alignment
\usepackage{subfig}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\begin{figure}[h]
	\centering
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_cosmo_cmb}
	} \hfill
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_brain_meg}
	} \hspace{0.1em}
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_climate_TMQ}
		\label{fig:examples:climate}
	} \hfill
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_daily_tmax}
	} \hfill
	\subfloat[]{
		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_graph}
	}
	\caption{
		Examples of intrinsically spherical data:
		(a) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
		(b) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
		(c) hourly precipitation from a climate simulation \citep{jiang2019sphericalcnn}, %\citep{mudigonda2017climateevents},
		(d) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
		%\todo{something from climate, weather?}
		%\todo{compare ideal full-spheres (like SHREC-17 projection from Esteves, 360 from Coors) to real-world measurements?}
		%\todo{horizontal colorbar for brain}
	}
	\label{fig:examples}
\end{figure}
\footnotetext[1]{\scriptsize\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
\footnotetext[2]{\scriptsize\url{https://martinos.org/mne/stable/auto_tutorials/plot_visualize_evoked.html}}

@@

\todo{
	* discuss discretizations (equiangular, HEALPix, icosahedral sphere) -> more uniform is better \\
	* no uniform sampling: tradeoffs have to be made \\
	* CNN vs FCN discussion (GAP for invariance) \\
}

@@

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ and $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.
The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}

\begin{table}
    \centering
	%\begin{tabular}{l cc r rr}
	\begin{tabular}{l cc r rS[table-format=2.0]}
		\toprule
		& \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
		& F1 & mAP & params & \multicolumn{1}{c}{inference} & \multicolumn{1}{c}{training} \\
		\midrule
		% $SO(3)$ vs $S^2$ vs graph
		\citet{cohen2018sphericalcnn} ($b=128$) & 78.9 & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.6 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
		\bottomrule
	\end{tabular}
    \caption{
		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
		% F1-score computed with sklearn, mAP from the official script of the competition.
		% inference speed = time for a single instance to do a single training pass
		% training speed = time for the neural net to train to peak performance
	}
    \label{tab:shrec17}
\end{table}
\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}

Results are shown in \tabref{shrec17}.
DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
% x times faster
As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}

@@

We evaluate our method on a task proposed by \citep{mudigonda2017climateevents}: the segmentation of extreme climate events, Tropical Cyclones (TC) and Atmospheric Rivers (AR), in global climate simulations (\figref{examples:climate}).
The data was produced by a 20-year run of the Community Atmospheric Model v5 (CAM5) and consists of 16 channels such as temperature, wind, humidity, and pressure at multiple altitudes.
We used the pre-processed dataset from \citep{jiang2019sphericalcnn}.\footnote{Available at \url{http://island.me.berkeley.edu/ugscnn/data}.}
%\url{https://github.com/maxjiang93/ugscnn}
%\url{https://github.com/maxjiang93/ugscnn/blob/master/experiments/exp4_sphere_climate/run.sh}
%\url{http://island.me.berkeley.edu/ugscnn/data/climate_sphere_l5.zip}
There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($N_{pix} = 10 \cdot 4^l + 2 = 10,242$).
The labels are heavily unbalanced with 0.1\% TC, 2.2\% AR, and 97.7\% background (BG) pixels.

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}

\begin{table}
	\centering
	\begin{tabular}{l l l}
	\toprule
	& accuracy & mAP \\
	\midrule
	%\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
	DeepSphere (weighted loss) & $97.8\pm 0.3$ & $77.15\pm 1.94$ \\
	DeepSphere (non-weighted loss) & $87.8\pm 0.5$ & $89.16\pm 1.37$ \\
	\bottomrule
	\end{tabular}
	\caption{
		Climate event segmentation results: mean accuracy (over TC, AR, BG) and mean average precision (over TC and AR).
		DeepSphere achieves state-of-the-art performance. %, suggesting again that anisotropic filters are an unnecessary price to pay.
	}
	\label{tab:climate}
\end{table}

Results are shown in \tabref{climate} (details in tables~\ref{tab:climate:accuracy}, \ref{tab:climate:map} and~\ref{tab:climate:speed}).
The mean and standard deviation are computed over 5 runs.
Note that while \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, it is not ideal for the mAP metric.
Results from \citet{mudigonda2017climateevents} cannot be directly compared as they don't use the same input channels.
DeepSphere achieves state-of-the-art performance, suggesting again that anisotropic filters are not necessary.

Compared to \citet{cohen2019gauge}'s conclusion, it is surprising that S2R does worse than DeepSphere (which is limited to S2S).
Potential explanations are (i) that their icosahedral projection introduces harmful distortions, or (ii) that a larger architecture can compensate for the lack of generality. % powerfulness?
We indeed observed that more feature maps and depth led to higher performance (\ref{sec:climate:appendix}).

@@

This work showed that DeepSphere strikes an interesting balance between desiderata for a spherical CNN.
A single parameter, the number of neighbors a pixel is connected to in the graph, controls the tradeoff between \todo{performance and efficiency}.
% vague words
As computational cost and memory consumption scales linearly with the number of pixels, DeepSphere easily deals with spherical maps made of millions of pixels.
Such high resolutions are not necessary to represent the depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
% That has to do with the frequency content of the signals (see fig xx)
% cannot do better
Also relevant in scientific applications is the flexibility offered by a graph representation to deal with partial coverage and non-uniform samplings.
% partial coverage / missing data
Finally, the implementation of Laplacian-based graph convolutions is straightforward.
The ubiquity of graph neural networks, pushing for a first-class support in Deep Learning frameworks, will make implementations even easier and more efficient.

A potential drawback of graph Laplacian-based approaches is that graph filters are isotropic, reducing the expressive power of the NN.
% in principle -> may in fact not
% Our experiments showed that DeepSphere nonetheless achieved state-of-the-art performance, on par with methods featuring anisotropic filters.
% didn't hurt perf in any experiment
% expressive power / generality / powerful / function approximator
%Why anisotropic filters?
Experiments from \citet{cohen2019gauge} suggest that more general convolutions achieve better performance.
Our climate experiments (\secref{exp:climate}) however show that DeepSphere achieves similar performance than their most general convolution.
% the SHREC17 experiment too shows that isotropic filters are sufficient
Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
% why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \todo{[Bronstein]} might also be explanations.
Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed for some applications.
% As was recently shown for graph NNs used for graph classification, most general might not be the best, when the ultimate goal is generalization [Andreas paper? + previous by xx]

@@

\section{Proof of theorem}\label{sec: appendix: proof of theorem}
Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal M$, a smooth function $f:\mathcal M \rightarrow \mathbb R$, and defined the vector $\b f$ of samples of $f$ as follows: $\b f\in \mathbb R^n,\ \b f_i = f(x_i)$, it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
where $L_n^t$ is defined as follows:
\begin{definition}{}\\
	\label{def:Heat Kernel Graph Laplacian operator}
	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
\end{definition}
Thus, to prove theorem \ref{theo:pointwise convergence for a regular sampling} it will be sufficient to prove that 
\begin{equation}\label{eq:continuous convergence}
 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} {L}_n^{t_n} f(y) =  \Delta_{\mathbb{S}^2}f(y)
\end{equation}
For the sake of the proof we will need also the following facts:
\begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$. We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\label{def:Functional approximation to the Laplace-Beltrami operator}
	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
\end{definition}

\begin{prop} (\cite{belkin2005towards}) \\
Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb R^N$, and fix $y\in\mathcal M$. Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$. Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$. Then
	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(y).$$
	\label{prop:3}
\end{prop}

% brief introduction:
This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}. This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

Our first goal is thus to prove the following Proposition:
\vspace{0.5cm}
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $||\cdot||$ with Lipschitz constant $\mathcal L_f$
	$$
	\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
	$$
	Furthermore, for all $y\in\mathbb S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
\end{prop}
\vspace{0.5cm}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c c r r}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.9ms & 47m \\
        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 0.9ms & 46m\\
        DeepSphere \emph{Improved HEALPix} & 80.76 & & &
    \end{tabular}
    \caption{Performance of different models}
    \label{tab:SHREC17_class}
\end{table}

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\begin{figure}[h]
	\includegraphics[height=0.25\linewidth]{example_cosmo_cmb}
	\hfill
	\includegraphics[height=0.25\linewidth]{example_brain_meg}
% 	\hfill
% 	\includegraphics[height=0.25\linewidth]{example_climate_TMQ}
	\hfill
	\includegraphics[height=0.25\linewidth]{example_ghcn_daily_tmax}
	\hfill
	\includegraphics[height=0.25\linewidth]{example_ghcn_graph}
	\caption{
		Examples of intrinsically spherical data:
		(left) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
		(middle) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
		(right) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, and the position of weather stations is arbitrary and changes over time.
		Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
		%\todo{something from climate, weather?}
		%\todo{compare ideal full-spheres (like SHREC-17 projection from Esteves, 360 from Coors) to real-world measurements?}
		%\todo{horizontal colorbar for brain}
	}
	\label{fig:examples}
\end{figure}
\footnotetext[1]{\scriptsize\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
\footnotetext[2]{\scriptsize\url{https://martinos.org/mne/stable/auto_tutorials/plot_visualize_evoked.html}}

@@

\todo{
	* discuss discretizations (equiangular, HEALPix) -> more uniform is better \\
	* no uniform sampling: tradeoffs have to be made \\
	* CNN vs FCN discussion (GAP for invariance) \\
}

@@

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ / $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.
The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}

\begin{table}%[ht]
    \centering
	%\begin{tabular}{l cc r rr}
	\begin{tabular}{l cc r rS[table-format=2.0]}
		\toprule
		& \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
		& F1 & mAP & params & \multicolumn{1}{c}{inference} & \multicolumn{1}{c}{training} \\
		\midrule
		% $SO(3)$ vs $S^2$ vs graph
		\citet{cohen2018sphericalcnn} ($b=128$) & 78.9 & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.6 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
		\bottomrule
	\end{tabular}
    \caption{
		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
		% F1-score computed with sklearn, mAP from the official script of the competition.
		% inference speed = time for a single instance to do a single training pass
		% training speed = time for the neural net to train to peak performance
	}
    \label{tab:shrec17}
\end{table}
\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}

Results are shown in \tabref{shrec17}.
DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} while being much more efficient, suggesting that anisotropic filters are an unnecessary price to pay.
% x times faster
As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}

@@

* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed\\
* cannot compare with Mudigonda (16 vs 1 input channel)\\
* (full: we scale (50B pixels, 20TB) $\Rightarrow$ lead to better perf?) \\

\begin{table}
	\centering
	\begin{tabular}{l l l}
	\toprule
	& accuracy & mAP \\
	\midrule
	\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
	DeepSphere (weighted loss) & $97.8\pm 0.3$ & $77.15\pm 1.94$ \\
	DeepSphere (non-weighted loss) & $87.8\pm 0.5$ & $89.16\pm 1.37$ \\
	\bottomrule
	\end{tabular}
	\caption{
		Climate event segmentation results: mean accuracy and mean average precision (mAP). DeepSphere achieves state-of-the-art performance while using isotropic filters (S2S in \citet{cohen2019gauge}'s language), suggesting again that anisotropic filters are an unnecessary price to pay.
		Note that \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, which is good for the accuracy metric (as it corrects for class imbalance) but bad for the mAP metric.
	}
\end{table}

* icosahedron dataset from \cite{jiang2019sphericalcnn} \\
* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
* cross entropy loss between parenthesis\\
* 5 runs for each loss to obtain mean and std\\
* same architecture as gauge, more feature maps than Jiang\\
* perf with same arch as Jiang in appendix => not enough channels!\\
* even more feature maps give us one more point in perf\\
* need more feature maps and layers to compensate for isotropy \\
* cannot compare with Mudigonda: not the same input data\\
* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling

* trade off between AP and accuracy in the case of TC class, it seems.\\
* change base, influence?\\

* full dataset not enough memory to run a correct model

% jiang like correct: 99.81631631, 13.18655162, 52.62412867, 55.20899887;  0.3990812 , 0.80056251, 0.59982186; 4 ms; 2h40
% more feat: 99.67871329, 38.78607557, 66.37910064, 68.2812965: 0.99981102, 0.60714174, 0.83236147, 0.71975161; 12ms; 6h20

@@

This work showed that DeepSphere strikes an interesting balance between desiderata for a spherical CNN.
A single parameter, the number of neighbors a pixel is connected to in the graph, controls the tradeoff between \todo{performance and efficiency}.
% vague words
As computational cost and memory consumption scales linearly with the number of pixels, DeepSphere easily deals with spherical maps made of millions of pixels.
Such high resolutions are not necessary to represent thethe  depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
% That has to do with the frequency content of the signals (see fig xx)
% cannot do better
Also relevant in scientific applications is the flexibility offered by a graph representation to deal with partial coverage and non-uniform samplings.
% partial coverage / missing data
Finally, the implementation of Laplacian-based graph convolutions is straightforward.
The ubiquity of graph neural networks, pushing for a first-class support in Deep Learning frameworks, will make implementations even easier and more efficient.

A potential drawback of graph Laplacian-based approaches is that graph filters are isotropic, reducing the expressive power of the NN.
% in principle -> may in fact not
% Our experiments showed that DeepSphere nonetheless achieved state-of-the-art performance, on par with methods featuring anisotropic filters.
% didn't hurt perf in any experiment
% expressive power / generality / powerful / function approximator
%Why anisotropic filters?
Experiments from \citet{cohen2019gauge} suggest that more general convolutions achieve better performance.
Our climate experiments (\secref{exp:climate}) however show that DeepSphere achieves similar performance than their most general convolution.
Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \todo{[Bronstein]} might also be explanations.
Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed for some applications.
% As was recently shown for graph NNs used for graph classification, most general might not be the best, when the ultimate goal is generalization [Andreas paper? + previous by xx]

@@

\section{Proof of theorem \ref{theo:pointwise convergence for a regular sampling}}\label{sec: appendix: proof of theorem}

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_Vf=\b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
	Note that we have the following relation $\b{L}_n^t \b{f} = T_V L_n^t f$.
	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
	\item 
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \mathbb R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$

\end{itemize}

Leaveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\cite{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).    
\end{equation}
\label{prop:3}
\end{prop}

\paragraph{Building the proof.}
As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse the second part or their proofs where \eqref{eq:Functional approximation to the Laplace-Beltrami operator} $\rightarrow$ \eqref{eq:laplace-beltrami}.
Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to a) show that 
\begin{equation}\label{eq:continuous convergence}
 \lim_{n\to\infty}L_n^{t} f(y) =  L^t(y)
\end{equation}
for a particular class of sampling and b) apply Proposition \ref{prop:3}.

%  \frac{|\mathbb{S}^2|}{4\pi t} 
% \begin{definition}{}\\
% 	\label{def:Heat Kernel Graph Laplacian operator}
% 	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
% 	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
% \end{definition}

% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
% where $L_n^t$ is defined as follows:

% For the sake of the proof we will need also the following facts:
% \begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$. We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
% 	\label{def:Functional approximation to the Laplace-Beltrami operator}
% 	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
% \end{definition}

% brief introduction:
% This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}. This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

We start by proving the following Proposition:
\vspace{0.5cm}
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
	$$
	\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
	$$
	Furthermore, for all $y\in\mathbb S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
\end{prop}
\vspace{0.5cm}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c c r r}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.9ms & 47m \\
        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 0.9ms & 46m\\
        % DeepSphere \emph{Improved HEALPix} & 80.76 & & &
    \end{tabular}
    \caption{Performance of different models}
    \label{tab:SHREC17_class}
\end{table}
